Water, High-Altitude Condensates, and Methane Depletion in the Atmosphere of the Warm Neptune WASP-107\lowercase{b}

### 2017-08-16 ms.tex
todo list

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/metalByMass.png}
\caption{Estimated envelope metallicity and core mass based on interior structure modeling of the mass and radius of WASP-107b. FIXME get new figure showing two ages.}
\label{fig:metal_prior}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/metalByAge.pdf}
\caption{Estimated envelope metallicity for a given core mass based on interior structure modeling. The red shading corresponds to the $3\sigma$ confidence interval for a young planet ($0.2-1$ Gyr); the blue is for an older age ($1-14$ Gyr).}
\label{fig:metal_prior}
\end{figure}
